Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-04-13 gullydiss.tex
include all formatting corrections suggested by R. Penman from his email on April 6, 2015, except for chapter 7 which is still in flux.
add content to Vita, trim Table caption in CS16 chapter

\usepackage[numbers]{natbib}

@@

\author{Michael Gully-Santiago}  	% Required

\address{
University of Texas at Austin \\
Department of Astronomy \\
2515 Speedway, Stop C1400 \\
Austin, Texas 78712-1205}  % Required

@@

\begin{vita}
Michael Gully-Santiago was born in Boston, MA.  He lives in Austin, TX.

\end{vita}

>>>>

\usepackage[numbers]{natbib}
\usepackage[nottoc]{tocbibind}

@@

\author{Michael Anthony Gully-Santiago}  	% Required

\address{igully@gmail.com}  % Required

@@

\begin{vita}
Michael Gully-Santiago was born in Boston, and attended high school in Norwell Massachusetts.  He matriculated at Boston University in 2003, where he earned a Bachelor of Arts in Astronomy \& Physics in May 2007.  During his undergraduate years he worked at the McDonald Observatory in Fort Davis, Texas and the Clay Center Observatory in Brookline, Massachusetts, where he remained as a faculty member until 2008.  He enrolled in the University of Texas at Austin Department of Astronomy's Graduate Program in August 2008.  In 2010 he was awarded the NASA Graduate Student Research Program fellowship, which enabled him to work at the NASA JPL Microdevices Laboratory in Pasadena, CA.  
\end{vita}
